The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
More updates to Section 3 -- still in progress

%\author[]{Mordechai Katzman}
%\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
%\email{M.Katzman@sheffield.ac.uk}

@@

Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  
In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$. 
These values are computed using the functions 
{\tt testIdeal} and {\tt FPureModule} from the \emph{TestIdeals} package
(CITE THE TEST IDEALS PACKAGE PAPER).
In fact, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^{t-\epsilon})$ is $R$, but  $\tau(R, f^t)$ is a proper ideal.  
Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\epsilon})$.  \textcolor{red}{These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.}

>>>>

@@

The function {\tt isFPT} determines whether a rational number is the $F$-pure threshold of a specified polynomial. 
Given a rational number $t$ and an element $f$ of a $\mathbb{Q}$-Gorenstein ring of characteristic $p>0$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise. 
The function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely, 
{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, $0$ when $t = \fpt(f)$ and $1$ when $t > \fpt(f)$.
Consider the following example, that illustrates this functionality.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i14 :             R = ZZ/11[x,y];

i15 :             f = x^3 + y^2;

i16 :             isFPT(9/11, f)

o16 = true

\end{MyVerbatim}
}
\medskip

In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$. 
These values are computed using the functions 
{\tt testIdeal} and {\tt FPureModule} from the \emph{TestIdeals} package
(CITE THE TEST IDEALS PACKAGE PAPER).
In fact, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^{t-\epsilon})$ is $R$, but  $\tau(R, f^t)$ is a proper ideal.  
Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\epsilon})$.  \textcolor{red}{These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.}
